Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-28 paper.tex
up

\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
\author{Chen Wang, Hui Ma, and Aaron Chen}
\institute{School of Engineering and Computer Science,
\\Victoria University of Wellington, New Zealand \\
Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}

@@

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform the evaluation. WSC09 provides problems with five tasks corresponding to variable number of services, and ontologies. Therefore, it is a challenge dataset for measuring the scalability of our quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation.

\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly. The $mt_{p}$ is set to 1 (Exact match) and 0.75 (Plugin). In general, weight settings and parameter match type quality are decided by users' preferences.

@@

The Table \ref{meanFitness} shows the mean fitness values of 30 independent runs accomplished by two methods. We employ statistical analysis to test the significant differences in mean fitness value. The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{WSC09} & PSO-based approach & GP-based approach  \\ \hline
Task 1                     &0.559207 $\pm$ 0.012780  $\uparrow$   &0.520659 $\pm$ 0.020758           \\ \hline
Task 2                     &0.470083 $\pm$  0.001106 $\uparrow$   &0.459681 $\pm$  0.002874          \\ \hline
Task 3                     & 0.550396 $\pm$ 0.012780              &0.567915 $\pm$ 0.023447 $\uparrow$   \\ \hline
Task 4                     & 0.468942 $\pm$ 0.001670  $\uparrow$  &0.431704 $\pm$ 0.009774            \\ \hline
Task 5                     & 0.469424 $\pm$ 0.000800  $\uparrow$  &0.245222 $\pm$ 0.036885            \\ \hline
\end{tabular}
\end{table}

>>>>

\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
\author{Chen Wang, Hui Ma, Aaron Chen and Sven Hartmann}
\institute{School of Engineering and Computer Science,
\\Victoria University of Wellington, New Zealand \\
Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}

@@

Web service challenge 2009 (WSC09) \cite{kona2009wsc} is a benchmark dataset consisting of five composition tasks that associated with an increasing number of services, and concepts in ontologies. An augmented version of WSC09 is utilised including QoS attributes for services, this version of WSC09 dataset is used in \cite{ma2015hybrid,da2016genetic}

The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly. The $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}. In general, weight settings and parameter match type quality are decided by users' preferences.

The first column of the table \ref{meanFitness} shows five tasks from WSC09 Dataset. The second and third column of the table \ref{meanFitness} show the orginal service repository size and shrunk service repository size after the greedy search respectively regarding the five tasks for the initialisation discussed in step 2 SubSect.\ref{PSO_based_approach}. These significant decreased number of services demonstrate that the researching space is effectively reduced. The fourth and fifth column of the table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods. We employ statistical analysis to test the significant differences in mean fitness value. The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l|l|l}
\hline
\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunk $SR$   &PSO-based approach & GP-based approach  \\ \hline
Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
Task 2                     &4129           &140   &0.4701 $\pm$ 0.0011  $\uparrow$  &0.4597 $\pm$ 0.0029          \\ \hline
Task 3                     &8138           &153   &0.5504 $\pm$ 0.0128              &0.5679 $\pm$ 0.0234 $\uparrow$   \\ \hline
Task 4                     &8301           &330   &0.4690 $\pm$ 0.0017  $\uparrow$  &0.4317 $\pm$ 0.0097            \\ \hline
Task 5                     &15211          &237   &0.4694 $\pm$ 0.0008  $\uparrow$  &0.2452 $\pm$ 0.0369            \\ \hline
\end{tabular}
\end{table}

@@
